Programming Fundamentals and Python

### 2007-07-04 slides/programming.tex
added new diagram on linguistic data types
svn/trunk@4816

\begin{verbatim}
  >>> from nltk.corpora import gutenberg
  >>> count = {}
  >>> for word in gutenberg.raw('shakespeare-macbeth'):
  ...     word = word.lower()
  ...     if word not in count:
  ...         count[word] = 0
  ...     count[word] += 1
\end{verbatim}

@@

\begin{verbatim}
  >>> from nltk.corpora import gutenberg
  >>> gutenberg.items
  ['austen-emma', 'austen-persuasion', 'austen-sense', 'bible-kjv', 'blake-poems', 'blake-songs', 'chesterton-ball', 'chesterton-brown', 'chesterton-thursday', 'milton-paradise', 'shakespeare-caesar', 'shakespeare-hamlet', 'shakespeare-macbeth', 'whitman-leaves']
  >>> count = 0
  >>> for word in gutenberg.raw('whitman-leaves'):
  ...     count += 1
  >>> print count
  154873
\end{verbatim}
\end{frame}

@@

\begin{verbatim}
  >>> from nltk.corpora import brown
  >>> brown.items
  ['a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'j', 'k', 'l', 'm', 'n', 'p', 'r']
  >>> from nltk.corpora import extract
  >>> print extract(0, brown.raw())
  ['The', 'Fulton', 'County', 'Grand', 'Jury', 'said', 'Friday', 'an', 'investigation', 'of', "Atlanta's", 'recent', 'primary', 'election', 'produced', '``', 'no', 'evidence', "''", 'that', 'any', 'irregularities', 'took', 'place', '.']
  >>> print extract(0, brown.tagged())
  [('The', 'at'), ('Fulton', 'np-tl'), ('County', 'nn-tl'), ('Grand', 'jj-tl'), ('Jury', 'nn-tl'), ('said', 'vbd'), ('Friday', 'nr'), ('an', 'at'), ('investigation', 'nn'), ('of', 'in'), ("Atlanta's", 'np$'), ('recent', 'jj'), ('primary', 'nn'), ('election', 'nn'), ('produced', 'vbd'), ('``', '``'), ('no', 'at'), ('evidence', 'nn'), ("''", "''"), ('that', 'cs'), ('any', 'dti'), ('irregularities', 'nns'), ('took', 'vbd'), ('place', 'nn'), ('.', '.')]
\end{verbatim}
\end{frame}

@@

\begin{verbatim}
  >>> from nltk.corpora import treebank
  >>> print extract(0, treebank.parsed())
  (S:
    (NP-SBJ:
      (NP: (NNP: 'Pierre') (NNP: 'Vinken'))
      (,: ',')
      (ADJP: (NP: (CD: '61') (NNS: 'years')) (JJ: 'old'))
      (,: ','))
    (VP:
      (MD: 'will')
      (VP:
        (VB: 'join')
        (NP: (DT: 'the') (NN: 'board'))
        (PP-CLR:
          (IN: 'as')
          (NP: (DT: 'a') (JJ: 'nonexecutive') (NN: 'director')))
        (NP-TMP: (NNP: 'Nov.') (CD: '29'))))
    (.: '.'))
\end{verbatim}
\end{frame}

>>>>

\begin{verbatim}
  >>> from nltk.corpus import gutenberg
  >>> count = {}
  >>> for word in gutenberg.read('shakespeare-macbeth'):
  ...     word = word.lower()
  ...     if word not in count:
  ...         count[word] = 0
  ...     count[word] += 1
\end{verbatim}

@@

\begin{verbatim}
  >>> from nltk.corpus import gutenberg
  >>> gutenberg.items
  ['austen-emma', 'austen-persuasion', 'austen-sense', 'bible-kjv', 'blake-poems', 'blake-songs', 'chesterton-ball', 'chesterton-brown', 'chesterton-thursday', 'milton-paradise', 'shakespeare-caesar', 'shakespeare-hamlet', 'shakespeare-macbeth', 'whitman-leaves']
  >>> count = 0
  >>> for word in gutenberg.raw('whitman-leaves'):
  ...     count += 1
  >>> print count
  154873
\end{verbatim}
\end{frame}

@@

\begin{verbatim}
  >>> from nltk.corpus import brown
  >>> brown.items
  ['a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'j', 'k', 'l', 'm', 'n', 'p', 'r']
  >>> print brown.read('a')[0]
  ['The', 'Fulton', 'County', 'Grand', 'Jury', 'said', 'Friday', 'an', 'investigation', 'of', "Atlanta's", 'recent', 'primary', 'election', 'produced', '``', 'no', 'evidence', "''", 'that', 'any', 'irregularities', 'took', 'place', '.']
  >>> print brown.tagged('a')[0]
  [('The', 'at'), ('Fulton', 'np-tl'), ('County', 'nn-tl'), ('Grand', 'jj-tl'), ('Jury', 'nn-tl'), ('said', 'vbd'), ('Friday', 'nr'), ('an', 'at'), ('investigation', 'nn'), ('of', 'in'), ("Atlanta's", 'np$'), ('recent', 'jj'), ('primary', 'nn'), ('election', 'nn'), ('produced', 'vbd'), ('``', '``'), ('no', 'at'), ('evidence', 'nn'), ("''", "''"), ('that', 'cs'), ('any', 'dti'), ('irregularities', 'nns'), ('took', 'vbd'), ('place', 'nn'), ('.', '.')]
\end{verbatim}
\end{frame}

@@

\begin{verbatim}
  >>> from nltk.corpus import treebank
  >>> print treebank.parsed('wsj_0001')[0]
  (S:
    (NP-SBJ:
      (NP: (NNP: 'Pierre') (NNP: 'Vinken'))
      (,: ',')
      (ADJP: (NP: (CD: '61') (NNS: 'years')) (JJ: 'old'))
      (,: ','))
    (VP:
      (MD: 'will')
      (VP:
        (VB: 'join')
        (NP: (DT: 'the') (NN: 'board'))
        (PP-CLR:
          (IN: 'as')
          (NP: (DT: 'a') (JJ: 'nonexecutive') (NN: 'director')))
        (NP-TMP: (NNP: 'Nov.') (CD: '29'))))
    (.: '.'))
\end{verbatim}
\end{frame}

\section{Miscellaneous Python Features}

\subsection{Character Encoding}

\begin{frame}
\begin{itemize}

\end{itemize}
\end{frame}
